Schramm-Loewner evolution in tricritical Ising model

### 2013-06-26 AffineLieAlgebras/Simons/paper.tex
Some text added

  We are interested in the case $A_4$, so we have
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.
The isotropic case $u=\lambda/2$ with boundary parameters
$u=\xi_1=\xi_2=\lambda/2$ corresponds to the  conformal point. Then we have
$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.

Bolzmann weights are
\begin{equation}
  \label{eq:4}
    \begin{array}{lllll}
    V_{-} &=& W\left.\left(
    \begin{array}{ll}
      2 & 3\\
      1 & 2
    \end{array}\right| u \right) &=&   W\left.\left(
    \begin{array}{ll}
      2 & 1\\
      3 & 2
    \end{array}\right| u
\right)=\frac{1}{\sqrt{2}} \frac{\sin(u)}{\sin(\lambda)}=\sin(u)\\
\end{equation}

\begin{itemize}
\item Boltzmann weights for $A_{4}$
\item Boundary weights ?
\item Critical point, isotropicity
\item Loop description (two types of loops, duality, similarity with dilute Ising model) 
\end{itemize}

>>>>

  We are interested in the case $A_4$, so we have
$2\cos\lambda=\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}}$,
$\lambda=0.62831853071796$ and $\psi=\left[1,2\cos\lambda,
  4\cos^2\lambda-1, 2cos\lambda-\frac{1}{2\cos\lambda}\right]$ or $\psi=\left[1,\frac{\sqrt{\sqrt{5}+3}}{\sqrt{2}},\frac{\sqrt{5}+1}{2},\frac{\sqrt{\sqrt{5}+3}\,\left( \sqrt{2}\,\sqrt{5}-\sqrt{2}\right) }{4}\right]$.

For simplicity we consider only the isotropic case $u=\lambda/2$ with boundary parameters
$u=\xi_1=\xi_2=\lambda/2$. This case in critical limit corresponds to the  conformal point. Then we have
$s_1(-u)=\frac{\sin\lambda/2}{\sin\lambda}=\frac{1}{2\cos\lambda/2}$ and $s_0(u)=\frac{1}{2\cos\lambda/2}$.

There are 14 configurations with Bolzmann weights:
\begin{equation}
  \label{eq:12}
  \begin{array}{l}
    W\left(                                          
        \begin{array}{cc}
          2 & 1 \\
          1 & 2
        \end{array}
      \right)=
    W\left(
        \begin{array}{cc}
          3 & 4 \\
          4 & 3
        \end{array}
      \right)=
\frac{\sqrt{2+\frac{2}{\sqrt{5}}}
      \left(3+\sqrt{5}\right) \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4}
          \left(1+\sqrt{5}\right)\right)\right)}{1+\sqrt{5}}\\
    W\left(                                      
        \begin{array}{cc}
          2 & 3 \\
          1 & 2
        \end{array}
      \right)=
    W\left(                                         
        \begin{array}{cc}
          3 & 2 \\
          4 & 3
        \end{array}
      \right)=    W\left(                                         
        \begin{array}{cc}
          3 & 4 \\
          2 & 3
        \end{array}
      \right)=    W\left(                                         
        \begin{array}{cc}
          2 & 1 \\
          3 & 2
        \end{array}
      \right)=\frac{2 \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4}
          \left(1+\sqrt{5}\right)\right)\right)}{\sqrt[4]{5}}\\
    W\left(                                         
        \begin{array}{cc}
          1 & 2 \\
          2 & 1
        \end{array}
      \right)= 
      W\left(                                                  
        \begin{array}{cc}
          4 & 3 \\
          3 & 4
        \end{array}
      \right)=\left(3+\sqrt{5}\right) \sqrt{\frac{1}{10}
      \left(5+\sqrt{5}\right)} \sin
    \left(\frac{1}{2}\cos^{-1}\left(\frac{1}{4}
        \left(1+\sqrt{5}\right)\right)\right) \\  
    W\left(                                       
        \begin{array}{cc}
          3 & 2 \\
          2 & 1
        \end{array}
      \right)=
    W\left(                                                       
        \begin{array}{cc}
          1 & 2 \\
          2 & 3
        \end{array}
      \right)=    W\left(                                                      
        \begin{array}{cc}
          4 & 3 \\
          3 & 2
        \end{array}
      \right)=
    W\left(                                                        
        \begin{array}{cc}
          2 & 3 \\
          3 & 4
        \end{array}
      \right)=\\
    \quad\quad\quad\sqrt{2+\frac{2}{\sqrt{5}}} \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4} \left(1+\sqrt{5}\right)\right)\right)\\
    W\left(
        \begin{array}{cc}
          3 & 2 \\
          2 & 3
        \end{array}
      \right)=    W\left(
        \begin{array}{cc}
          2 & 3 \\
          3 & 2
        \end{array}
      \right)=2 \sqrt{2+\frac{2}{\sqrt{5}}} \sin \left(\frac{1}{2} \cos^{-1}\left(\frac{1}{4} \left(1+\sqrt{5}\right)\right)\right)\\

  \end{array}
\end{equation}

We see the duality under the exchange $1\leftrightarrow 4, 2\leftrightarrow 3$.

Boundary weights are in correspondence with the choice of boundary
conditions. Possible integrable boundary conditions and boundary
weights were identified in \cite{behrend2001integrable}.

The $A_4$ RSOS model admits following loop description. Consider odd
sublattice with values at sites equal to $1,3$ and draw loops around
$4$s on it. Then consider even sublattice and draw loops around $1$s.
The loops do not intersect. Loop picture characterizes configuration
up to duality.

Consider following boundary condition:
\begin{equation}
  \label{eq:13}
  \underline{\begin{array}{llllllllll}
    & 3 & & 1 &  & 3 & - & 3 & & \\
    2 & & 2 &  & 2 & | & 4 & | & 2\\
    & 1 & & 3 & - & 3 & & 3 &- & \\
    2 & & 2 & | & 4 & & 4 & & 4\\
    &  3 & & 3 &- & 3 &- & 3 &- &\dots
  \end{array}}
\end{equation}
There is obviously an interface on double lattice delimiting $2$-s from $4$-s. We analyze the

\begin{itemize}
\item Boundary weights ?
\item Loop description (two types of loops, duality, similarity with dilute Ising model) 
\end{itemize}
